\begin{resumo}[Abstract]
 \begin{otherlanguage}{english}

 The digital gaming industry emerges as a powerful protagonist on the global stage, surpassing even the film sector in terms of impact and reach. In 2021, while the film market recorded a revenue of US\$ 90.9 billion \cite{global_films_musics_market}, the global gaming industry reached a remarkable milestone of US\$ 192.7 billion in the same period \cite{global_games_market}. This exponential growth highlights the massive appeal of games, representing a significant cultural shift where consumers dedicate a substantial portion of their time to this form of interactive entertainment. In this dynamic context, \textit{GameLocker} emerges as a response to the growing demand for more organized and socially engaging gaming experiences. Understanding the need to provide a centralized location for the storage and organization of game libraries, as well as an interactive and user-friendly space, \textit{GameLocker} stands out as a crucial innovation. Besides simplifying game management, the platform aims to create a cohesive global community where players from different geographical backgrounds can connect and share their common passions. By fostering social interaction in a digital environment, \textit{GameLocker} not only facilitates friendly competitions but also promotes a rich exchange of experiences among players. By offering a practical solution while simultaneously cultivating an environment that nurtures the passion and engagement of gamers, \textit{GameLocker} positions itself as an initiative fully aligned with the needs and desires of the growing global community of gaming enthusiasts.

    \vspace{\onelineskip}

    \noindent 
    \textbf{Keywords:} digital gaming industry, impact and reach, game management, social interaction, game enthusiasts.
    \end{otherlanguage}
 
\end{resumo}

\pagebreak